1st Revision

### 2019-04-06 Report/first-revision.Rmd
Adds a bit of normalised vs absolute results!

### Experiment 1 phase 1
```{r}
summary(aov(abs_error ~ learning.condition, data = sub_sop_all[sub_sop_all$phase == 1, ]))
ggplot(sub_sop_all[sub_sop_all$phase == 1, ], aes(learning.condition, abs_error)) +
  stat_summary(fun.data=mean_cl_normal,position=position_dodge(0.95), geom="errorbar") + 
  stat_summary(fun.y=mean,position=position_dodge(width=0.95),geom="bar")
```

### Experiment 1 phase 2
```{r}
summary(aov(abs_error ~ learning.condition, data = sub_sop_all[sub_sop_all$phase == 2, ]))
ggplot(sub_sop_all[sub_sop_all$phase == 2, ], aes(learning.condition, abs_error)) +
  stat_summary(fun.data=mean_cl_normal,position=position_dodge(0.95), geom="errorbar") + 
  stat_summary(fun.y=mean,position=position_dodge(width=0.95),geom="bar")
```

@@

### Experiment 2 phase 1
```{r}
summary(aov(abs_error ~ learning.condition, data = sub_sop_all_2[sub_sop_all_2$phase == 1, ]))
ggplot(sub_sop_all_2[sub_sop_all_2$phase == 1, ], aes(learning.condition, abs_error)) +
  stat_summary(fun.data=mean_cl_normal,position=position_dodge(0.95), geom="errorbar") + 
  stat_summary(fun.y=mean,position=position_dodge(width=0.95),geom="bar")
```

### Experiment 2 phase 2
```{r}
summary(aov(abs_error ~ learning.condition, data = sub_sop_all_2[sub_sop_all_2$phase == 2, ]))
ggplot(sub_sop_all_2[sub_sop_all_2$phase == 2, ], aes(learning.condition, abs_error)) +
  stat_summary(fun.data=mean_cl_normal,position=position_dodge(0.95), geom="errorbar") + 
  stat_summary(fun.y=mean,position=position_dodge(width=0.95),geom="bar")
```

@@

### Both experiments split by final condition
```{r}
summary(aov(abs_error ~ type, data = sop_all[sop_all$phase == 2, ]))
ggplot(sop_all[sop_all$phase == 2, ], aes(type, abs_error)) +
  stat_summary(fun.data=mean_cl_normal,position=position_dodge(0.95), geom="errorbar") + 
  stat_summary(fun.y=mean,position=position_dodge(width=0.95),geom="bar")
```

@@

>>>>

### Experiment 1 phase 1
```{r}
av <- aov(abs_error ~ learning.condition, data = sub_sop_all[sub_sop_all$phase == 1, ])
summary(av)
apa_print(av)$full_result$learning_condition
ggplot(sub_sop_all[sub_sop_all$phase == 1, ], aes(learning.condition, abs_error)) +
  stat_summary(fun.data=mean_cl_normal,position=position_dodge(0.95), geom="errorbar") + 
  stat_summary(fun.y=mean,position=position_dodge(width=0.95),geom="bar")
```

### Experiment 1 phase 2
```{r}
av <- aov(abs_error ~ learning.condition, data = sub_sop_all[sub_sop_all$phase == 2, ])
summary(av)
apa_print(av)$full_result$learning_condition
ggplot(sub_sop_all[sub_sop_all$phase == 2, ], aes(learning.condition, abs_error)) +
  stat_summary(fun.data=mean_cl_normal,position=position_dodge(0.95), geom="errorbar") + 
  stat_summary(fun.y=mean,position=position_dodge(width=0.95),geom="bar")
```

@@

### Experiment 2 phase 1
```{r}
av <- t.test(abs_error ~ learning.condition, data = sub_sop_all_2[sub_sop_all_2$phase == 1, ])
summary(av)
apa_print(av)$full_result
ggplot(sub_sop_all_2[sub_sop_all_2$phase == 1, ], aes(learning.condition, abs_error)) +
  stat_summary(fun.data=mean_cl_normal,position=position_dodge(0.95), geom="errorbar") + 
  stat_summary(fun.y=mean,position=position_dodge(width=0.95),geom="bar")
```

### Experiment 2 phase 2
```{r}
av <- t.test(abs_error ~ learning.condition, data = sub_sop_all_2[sub_sop_all_2$phase == 2, ])
apa_print(av)$full_result
ggplot(sub_sop_all_2[sub_sop_all_2$phase == 2, ], aes(learning.condition, abs_error)) +
  stat_summary(fun.data=mean_cl_normal,position=position_dodge(0.95), geom="errorbar") + 
  stat_summary(fun.y=mean,position=position_dodge(width=0.95),geom="bar")
```

@@

### Both experiments split by final condition
```{r}
av <- aov(abs_error ~ type, data = sop_all[sop_all$phase == 2, ])
summary(av)
apa_print(av)$full_result$learning_condition
ggplot(sop_all[sop_all$phase == 2, ], aes(type, abs_error)) +
  stat_summary(fun.data=mean_cl_normal,position=position_dodge(0.95), geom="errorbar") + 
  stat_summary(fun.y=mean,position=position_dodge(width=0.95),geom="bar")
```

@@

## Absolute vs normalised values 
```{r}
b4 <- only_blocks(sub_walk_all, c(4))
apa_print(aov(b4$distance ~ b4$learning.condition))$full_result$b4_learning_condition
apa_print(aov(b4$min_norm_distance ~ b4$learning.condition))$full_result$b4_learning_condition
b4 <- only_blocks(sub_walk_all, c(6))
apa_print(aov(b4$distance ~ b4$learning.condition))$full_result$b4_learning_condition
apa_print(aov(b4$min_norm_distance ~ b4$learning.condition))$full_result$b4_learning_condition
```

## Gender effects

## NEw charts
